Background for transient faults in asynchronous circuits

### 2019-04-07 draft_together3.tex
up to lemma 2

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\section{Normal operation analysis}
As mentioned in the previous section on Speed Independent circuits, circuits can be modeled by a state graph.  
We want to define a trace, to describe the different paths a circuit can take as it follows the state graph.  Different paths can occur because there are states with multiple transitions from that state.  We record the succession of states and transitions by the trace which is defined as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $\sigma_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(\sigma_i,\sigma_{i+1})$ for $\forall i \in \mathbb{N}$.\end{definition} 
Even if there is only one transition from each state of a state graph, that is a linear state graph, our definition of trace is consistent with that.  \\
%add finite traces
% all states or just the state graph ones

@@

As mentioned in the previous paragraph, the internal wires The initial state in the original circuit must be assigned wire values that is consistent with semi-modularity.  For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.  The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s. The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.  Given these we will show how to define a corresponding initial state in the duplicated circuit.  %should I delete intermediate?
\begin{definition} A {\em valid initial state} for the A half of a duplicated circuit is defined as follows.  Given any initial state in the original circuit $s \in S$, assume that for each wire $w$, the wire values within the logic blocks are consistent with the semi-modularity property.  Assign the wire values within the logic block to corresponding wires in the half duplicated circuit.  Then assign the value $w$ to corresponding wires in the half duplicated circuit so that $w=c1^A=c2^A=c3^A=w^A$. The same assignment of wire values can also be applied for the B half of a duplicated circuit.
\end{definition}
%\textbf{
For all subsequent discussion in this document, when we talk about the trace of a duplicated circuit we assume that both sides start from the same valid initial state.  I will not include this assumption in the following lemma definitions to avoid complicated wording.  %}  
However for Lemma 1 we only require one half to start from a valid initial state.  
One additional assumption we make about the gates and wire values (including in the presence of faults) are that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the incoming wires.\\

\begin{lemma}[1]
Let $\sigma_n$ be the sequence of the first n states of a trace $\sigma$ in the duplicated circuit (the trace is possibly finite).  If a trace $\sigma$ starts from a valid initial state in the half circuit A, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit.  By symmetry this is also satisfied for the half circuit B.

@@

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
\begin{proof}
Without loss of generality we prove that this property holds for the A half of the circuit, the same reasoning can then be applied to the B half of the circuit.  We prove this lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is
\begin{itemize}
\item For a length $n$ sequence $\sigma_n$ in the duplicated circuit, this maps to $h^{A}(\sigma_n)$, a prefix of a trace of the original circuit.
\item Every logic block is in a Semi-Modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s_k$ of $\sigma_n$ it is true that a wire $w$ in the original circuit of state $h^A(s_k)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  The case where two or more of the three conditions being true does not exist in this setting.  As a consequence a wire $w$ is unexcited if and only if none of the previous three conditions are true. \\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses holds for any valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit from its construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the wire values so that the logic blocks are in a Semi-Modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and the duplicated half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit (the logic block output is excited).  Together with the definition of the valid initial state $c1^A=c2^A=c3^A=w^A$ (no excitations within the C-element chain), if $w$ is excited in $h^A(s_k)$, then only $c1^A$ is excited.  Conversely if $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$ then $w$ is excited in $h^A(s_k)$.  All C-element chains in the duplicated have at most one wire in the chain excited. This shows the initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the sequence of the first $k$ states in a trace (for traces length greater than or equal to $k$).  We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.  In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.  Then we show that for all possible $s_{k+1}$ logic block remains in a Semi-Modularity consistent state.  Finally for all wires in $s_{k+1}$, the second induction hypothesis is true.\\

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in $h^A(s_k)$ and its corresponding wires in the A-half $s_k$.  For each excited wire $w$, the last induction hypothesis narrows the possible cases and we examine the next state if a transition occurs in each case. %logic gate excited = c1^A excited
\begin{itemize}
\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, which satisfies the third induction hypothesis for wire $w$.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires which are also inputs to logic blocks did not change so the logic blocks are in a Semi-Modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus the third induction hypothesis is true for wire $w$.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.   
\item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus the third induction hypothesis is true for wire $w$.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition under this case.

\item The fourth case is when the signal propapagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a valid state in the original Semi-Modular circuit and the A-half logic blocks at state $s_k$ are Semi-Modularity consistent, inputs to all logic blocks in the A-half are also Semi-Modularity consistent. Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by Semi-Modularity)  
\begin{itemize}
\item
$w$ is unexcited in state $h^A(s_{k+1})$ (if we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.  Since $w$ is now unexcited, wire $w$ does not contradict the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by Semi-Modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, this does not contradict the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, that is not excited in $h^A(s_k)$, then in states $s_{k}$ and $s_{k+1}$,  $c1^A=c2^A=u^A$.  But since $u$ is excited then $c1^A$ of $u$ is excited.  Thus the third induction hypothesis holds for these wires $u$ as well.  
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, logic gate is not excited and $c1^A=c2^A=c3^A=u^A$ and the third induction hypothesis holds for these wires.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

@@

Note that the previous proof does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g. does not cause hazards in the C-element output).  Thus this lemma is true regardless of whether there is a fault or not in the other half of the circuit.  It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.  Next we will show that if both halves of the circuit start at the same valid initial state, deadlock does not occur.

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For all traces $\sigma$ in the duplicated circuit (for both halves starting in the same valid initial state), for any state in a trace, all wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the duplicated circuit, each wire block will be in one of the cases in the above figure.  The figure halves the number of cases, case 11 is the inversion of case 1 (the 0's and 1's inverted) and after case 11 the state transition goes through the second half of the cases with figure \ref{fig:l21} inverted.  Thus we only need to analyze up to case 10.  Because both halves satisfy the conditions of lemma 1, those properties can be applied directly.\\

>>>>

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\section{Normal operation analysis}
As mentioned in the previous section on Speed Independent circuits, circuits can be modeled by a state graph.  
We want to define a trace, to describe the different paths a circuit can take as it follows the state graph.  Different paths can occur because there are states with multiple transitions from that state.  We record the succession of states and transitions by the trace which is defined as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $s_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(s_i,s_{i+1})$ for $\forall i \in \mathbb{N}$.  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$$\end{definition} 
Even if there is only one transition from each state of a state graph, that is a linear state graph, our definition of trace is consistent with that.  \\
%add finite traces
% all states or just the state graph ones

@@

The initial wire values of a circuit is equally important.  In the original circuit, all states of a trace are states in the underlying state graph.  In particular the initial wire values corresponding to the initial state $s$ must also be a state in the underlying state graph.  In addition, as mentioned in the previous paragraph, the internal wires at the initial state (and each state thereafter) must be semi-modularity consistent.   The fault tolerant circuit must be initialized in a similar way.  We introduce one possible initialization for the fault tolerant circuit based on the initialization of the original circuit.  This covers how to initialize both the duplicated copies as well as the extra $c1^A$, $c1^B$, $c2^A$, $c2^B$, $c3^A$, $c3^B$ wires that are introduced.
%For all initial states we assume that we know the values of every wire in the circuit, intermediate and visible wires.  The visible wire values are the output wires in the circuit $w$, and the wires $c1$, $c2$ and $c3$'s. The intermediate wires are all other wires, which consists of all the wires within the logic blocks for each output wire.  Given these we will show how to define a corresponding initial state in the duplicated circuit.  %should I delete intermediate?
\begin{definition} A {\em valid initial state} for the A half of the fault tolerant circuit is constructed as follows.  Given any state in the original circuit state graph $s \in S$, assume that there exists initial wire values that correspond to $s$.  In addition, for each wire $w$, the internal wire values within the logic block of $w$ are semi-modularity consistent.  Construct the valid initial state by copying the internal wire values to corresponding internal wires in the A half circuit.  Then assign the value $w$ to appropriate wires in the A half circuit such as $w=c1^A=c2^A=c3^A=w^A$. The same construction can be applied for the B half circuit as well.
\end{definition}
%\textbf{
For all subsequent discussion in this document, when we talk about the trace of a fault tolerant circuit we assume that both half circuits start from the same valid initial state.  I will not include this assumption in the following lemma definitions to avoid complicated wording.  %}  
The one exception is for Lemma 1 where we only require one half circuit to start from a valid initial state.  \\

One additional assumption that we make about the gates and wire values (including in the presence of faults) is that wire values are strictly 0 or 1, and transitions from excited gates also only produce 0 or 1 and no in between values, no matter the duration of signals from the input wires.\\

\begin{lemma}[1]
If the A half of the fault tolerant circuit starts in a valid initial state, and where $\sigma$ is the trace of the fault tolerant circuit, then $h^{A}(\sigma_n)$ is a prefix of a trace of the original circuit, regardless of the wire values in the B half.  The trace $\sigma$ can be finite or infinite in length.  
%Let $\sigma_n$ be the sequence of the first $n$ states of a trace $\sigma$ of the fault tolerant circuit (the trace is possibly finite).  
By symmetry this is also true for the B half if we exchange A and B in the statement above.

@@

%If the duplicated circuit is in state $s_n$ and the original circuit is in state $h^A(s_n)$, and for all wires $w$ that are excited in this state $f_w(s_n|_I)\neq w$ in original circuit, then $f_w(s_n|_I) \neq x^A$ or $x^A \neq w^A$ in duplicated circuit (exactly one of these is true).  
%In addition, if wire $w$ is not excited in the original circuit $f_w(s_n|_I)=w$, then in the duplicated circuit half $f_w(s_n|_I)=x^A=w^A$.  
\end{lemma}
\begin{proof}
Without loss of generality we prove that this property holds for the A half, the same reasoning can then be applied to the B half.  We prove this lemma by induction on all traces of the circuit of length $n$.  The induction hypothesis is:
\begin{itemize}
\item Assume that $\sigma$ is a trace in the fault tolerant circuit.  Then $\sigma_n$ maps to $h^{A}(\sigma_n)$, which is a prefix of a trace of the original circuit.
\item Every logic block is in a semi-modularity consistent state.  %newly added, a new property outside of \sigma_n mapping to h^A(\sigma_n)
\item In every state $s$ of $\sigma_n$, it is true that a wire $w$ in the original circuit of state $h^A(s)$ is excited if and only if exactly one of the following is true: $c1^A$ is excited or $c1^{A}\neq c2^{A}$ or $c2^{A}\neq c3^A$ or $c3^{A}\neq w^A$ (the new value is propagating down one of the logic block or chain of C-elements).  The case where two or more of the three conditions being true does not exist in this setting.  Also a wire $w$ is unexcited if and only if none of the four excited conditions are true. \\
%Proving any two of the above three statements is equivalent to the third being true as well.% also I'm calling h^A(s_k) to mean the unduplicated circuit with these states assigned.... forget if I explained or not
\end{itemize}
% true but needs to find a new home -> either $h^A(s_n)=h^A(s_{n+1})$ or $T(h^A(s_n), h^A(s_{n+1}))$
We show in the base case that the induction hypotheses hold for any state in the fault tolerant circuit constructed from a valid initial state (ie. all possible traces of length 1). 
\begin{itemize}
\item For every $s_1$ that is a valid initial state we have that $h^A(s_1)$ is some state in the original circuit by its construction.  Thus $h^A(s_1)$ is a prefix of size 1 of a trace in the original circuit.  
\item We assigned the wire values so that the logic blocks are in a semi-modularity consistent state.  
\item For any wire $w$, since the input wire values are identical in the original circuit and in the A half and $c1^A=w$ then $c1^A$ is excited if and only if $w$ is excited in the original circuit.  This case can also interpreted as the logic block being excited.  Additionally there are no excitations within the C-element chain because in the valid initial state assignment $c1^A=c2^A=c3^A=w^A$.  As a result, $w$ is excited in $h^A(s_k)$ if $c1^A$ is excited in the A half.  By similar logic, for unexcited wires in the original circuit, the corresponding $c1^A$ is not excited and $c1^A=c2^A=c3^A=w^A$ from the initial assignment.  This shows the valid initial state also satisfies the last part of the induction hypothesis.    %is this enough.... that the existing states follow that iff statement?
\end{itemize}

The induction step is to assume that the induction hypotheses is true for $\sigma_k$, the subsequence for a trace $\sigma$ with length greater than or equal to $k$.  We will prove that the induction hypothesis is also true for $\sigma_{k+1}$, if it exists.  In particular for all possible $s_{k+1}$ we show that either $h^A(s_{k})=h^A(s_{k+1})$ or $T(h^A(s_{k}),h^A(s_{k+1}))$ to satisfy the first induction hypothesis.  Then we show that for all possible $s_{k+1}$ logic block remains in a semi-modularity consistent state.  Finally for all wires in $s_{k+1}$, the third induction hypothesis is true.\\

From state $s_k$, we look at all possible transitions; a transition may only occur on excited gates or c-elements.  If the transition occurs on the other half then no wire values changed in the A-half and the induction hypothesis remain true.  Thus we only need to consider the wires $w$ which are excited in the original circuit in state $h^A(s_k)$ and its corresponding wires in the A-half circuit.  For each excited wire $w$, the last induction hypothesis narrows the possible wires that can be excited in state $s_k$ and we examine the properties of the next state for each transition that can occur. %logic gate excited = c1^A excited
%possibly add graph to illustrate this
\begin{itemize}
\item The first case is for an excited wire $w$, the corresponding $c1^A$ is excited and $c1^A=c2^A=c3^A=w^A$, then $c1^A$ transitions.  Then in $s_{k+1}$, the only changes are that $c1^A$ is no longer excited and $c1^A\neq c2^A$, thus wire $w$ satisfies the third induction hypothesis.  Since the transition occurred on an intermediate wire, the set of excited wires in state $h^A(s_{k+1})$ of the original circuit does not change and for both excited wires $v$ where $v\neq w$ and not excited wires the third induction hypothesis carries over from $s_k$ to $s_{k+1}$.  Thus the third induction hypothesis is true for all output wires.  Also since the output wires did not change, then $h^A(s_k)=h^A(s_{k+1})$ satisfying the first induction hypothesis.  The output wires not changing also allow the logic blocks to stay in a semi-modularity consistent state.   The induction hypotheses are true for any transition from this case.  %don't know if this needs to be explained more (and add that the non-excited wires are still non-excited?)
%since the inputs to the gate and the intermediate wires did not transition, then the gate is excited or $y^{A,B}\neq v^{A,B}$.  
%do I need to show that non-excited has nothing excited in duplicated
%$w$ is still excited in $h^A(s_{k+1})$ and in state $s_{k+1}$ only $c1^{A}\neq c2^{A}$ is true.   Therefore in this case the property is true for state $s_{k+1}$
\item The second case is when the signal propapagates down to $c2^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^{A}\neq c2^{A}$ and $c2^A=c3^A=w^A$, then $c2^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c1^A=c2^A$ and $c2^{A}\neq c3^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.   
\item The third case is similar to the second case and occurs when the signal propapagates down to $c3^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A$, $c2^{A}\neq c3^{A}$ and $c3^A=w^A$, then $c3^A$ transitions.  
Then in state $s_{k+1}$, the changes are $c2^A=c3^A$ and $c3^{A}\neq w^{A}$ and thus wire $w$ satisfies the third induction hypothesis.  This is also an intermediate wire transition so by similar reasoning to the first case, all induction properties are true for any transition from this case.

\item The fourth case is when the signal propapagates down to $w^A$.  In state $s_k$, $c1^A$ is unexcited, $c1^A=c2^A=c3^A$ and $c3^A\neq w^A$, then $w^A$ transitions.  Since $w$ is excited in $h^A(s_k)$, then $T(h^A(s_k), h^A(s_{k+1}))$ which satisfies the first induction hypothesis.  Also since $h^A(s_{k+1})$ is a state in the original semi-modular circuit and the A-half logic blocks at state $s_k$ are semi-modularity consistent, inputs to all logic blocks in the A-half are also semi-modularity consistent. Then we look at the third induction hypothesis by splitting all of the wires into 4 subcases: the transitioning wire $w$; excited wires in state $h^A(s_k)$ other than $w$; newly excited wires in state $h^A(s_{k+1})$; and wires that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$.  (excited wires in $h^A(s_k)$ cannot be unexcited in $h^A(s_{k+1})$ by the semi-modularity property)  
\begin{itemize}
\item
$w$ is unexcited in state $h^A(s_{k+1})$ (we disregard the possibility that w can be immediately excited again), and in the A-half the changes are that $c3^{A}= w^{A}$.  Thus $w$ is unexcited and also the corresponding wires in the fault tolerant circuit are unexcited, wire $w$ satisfies the third induction hypothesis.  
\item
For any excited wire $v$ in state $h^A(s_k)$ and $v\neq w$, by semi-modularity of the original circuit $v$ is excited in state $h^A(s_{k+1})$ as well.  Thus, $c1^A$ of $v$ will not change its excitation state in $s_{k+1}$ and the rest of the corresponding wires of $v$ stays the same, wires of this type satisfy the third induction hypothesis.  
\item
For all newly excited wires $u$ in $h^A(s_{k+1})$, then in state $s_{k}$ $u$ is not excited in $h^A(s_k)$ and $c1^A=c2^A=c3^A=u^A=u$ and this is true in $s_{k+1}$ as well.  But since $u$ is excited then $c1^A$ in the A half must be excited.  Thus wires of this type satisfy the third induction hypothesis. 
\item
Finally for all other wires, ones that are unexcited in both $h^A(s_k)$ and $h^A(s_{k+1})$, the logic gate is not excited and $c1^A=c2^A=c3^A=u^A$.  Thus wires of this type satisfy the third induction hypothesis.  
\end{itemize}
Then the induction hypotheses are true for any transition from this case. 
\end{itemize}
So the induction hypotheses holds for all possible $\sigma_{k+1}$ and the induction step is complete. \\
By induction on the length of the trace, the first property shows that $h^{A,B}(\sigma_n)$ is the prefix of a trace from the original circuit for all n.
%do I need to show the opposite?  At every step the previous transitions are possible??  Dunno if true for faults though.... also something about collapsed states can't tell the difference?  Can we just map it to a circuit where everything goes together? <- this needs proving?

@@

Note that the previous proof does not place any restrictions on the other half of the circuit other than that it does not break the digital abstraction for the C-elements that has inputs from both halves of the circuit (e.g. does not cause hazards in the C-element output).  Thus this Lemma is true regardless of whether there is a fault or not in the other half of the circuit.  It guarantees that if there is a next state it must follow the state transitions of the original circuit, but does not guarantee that there will be a next state.  %maybe move this to in front of L1
Next we will show that if both halves of the circuit start at the same valid initial state, deadlock does not occur.

\begin{figure}
  \centering
    \includegraphics{flowl2c3}
  \caption{The wires in each row are in order of logic block, C1, C2, C3, W.  Each row represents half of the duplicated circuit, ie. top row are A half wires and bottom row are B half wires.  'Un' denotes that the logic block is unexcited and 'Exc' denotes the logic block is excited.  Blue arrows indicate a case change caused by transitions elsewhere in the circuit.  Black arrows indicate a wire transition.}
  \label{fig:l21}
\end{figure}
%fixed 
\begin{lemma}[2.1]
For any state in a trace $\sigma$ of the fault tolerant circuit starting in a valid initial state, all wire blocks are in one of the cases in figure \ref{fig:l21}.
\end{lemma}
\begin{proof}
We show by induction that for the fault tolerant circuit, each wire block will be in one of the cases in the above figure.  The figure halves the number of cases, case 11 is the inversion of case 1 (with the 0's and 1's inverted) and from case 11 the state transition goes through the second half of the cases in figure \ref{fig:l21} but inverted.  Thus we only need to analyze up to case 10.  Because both halves satisfy the conditions of Lemma 1, those properties can be applied directly.\\
